Local to Global Mariculture Modelling

### 2025-08-01 index.qmd
Analysis updates

library(magrittr)
library(units)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(ggh4x)
library(here)
library(ggpubr)
library(cowplot)
library(patchwork)
library(qs)
library(arrow)
library(targets)
library(sf)
library(terra)
library(rnaturalearth)
library(rnaturalearthdata)
library(rnaturalearthhires)
library(dtplyr)
library(furrr)
library(purrr)
library(future)
library(readxl)
library(conflicted)
library(lubridate)
library(RColorBrewer)
conflicts_prefer(dplyr::select(), dplyr::filter(), dplyr::intersect())
# This markdown uses TinyTex - install with tinytex::install_tinytex()

@@

```{r global-variables}
#| include: false
#| cache: false

@@

feed_pal <- c(
  "past" = "#E41A1C", 
  "reference" = "#377EB8", 
  "future" = "#4DAF4A",
  "plant_dominant" = "#4DAF4A",
  "marine_dominant" = "#377EB8",
  "novel_inclusive" = "#E41A1C"
)
cohort_pal <- c("1" = "#E41A1C", "2" = "#377EB8", "3" = "#4DAF4A", "all" = "black")
macro_pal <- c(
  "protein" = "darkred", 
  "P" = "darkred", 
  "carbohydrates" = "steelblue", 
  "C" = "steelblue", 
  "lipids" = "darkgoldenrod1", 
  "L" = "darkgoldenrod1"
)

@@

@@

```{r}
#| label: sens-results

sens_results_files <- file.path(output_sens_data_path) %>% 
  list.files(full.names = T) %>% 
  str_subset("results")
```

```{r}
#| label: input-data

ins_P <- list.files(per_biomass_cohort_path, full.names = T) %>% 
  str_subset("P_uneat|P_excr") %>% 
  purrr::map(function(nm) {qs::qread(nm)}) %>% 
  bind_rows()

ins_tot <- list.files(per_biomass_cohort_path, full.names = T) %>% 
  str_subset("total_uneat|total_excr") %>% 
  purrr::map(function(nm) {qs::qread(nm)}) %>% 
  bind_rows()
```

## Total inputs (uneaten and excreted)

### Through time

```{r}
#| label: fig-uneat-excr-plot-ts
#| fig-cap: Initial look at excreted and uneaten through time

ins_tot %>% 
  mutate(t = t-365) %>% 
  merge(farm_geometry, by.x = "farm_ID", by.y = "farm_id") %>% 
  group_by(country, feed, t, measure) %>% 
  reframe(
    sd_perbiom = sd(mean_perbiom),
    mean_perbiom = mean(mean_perbiom)
    ) %>% 
  mutate(
    mean_perbiom = mean_perbiom %>% 
      set_units("g g_fish-1") %>% 
      set_units("kg t_fish-1"),
    sd_perbiom = sd_perbiom %>% 
      set_units("g g_fish-1") %>% 
      set_units("kg t_fish-1")
  ) %>% 
  ggplot(aes(
    x = t, 
    y = drop_units(mean_perbiom), 
    ymin = drop_units(mean_perbiom-sd_perbiom), 
    ymax = drop_units(mean_perbiom+sd_perbiom), 
    colour = feed, 
    fill = feed
  )) +
  geom_line() +
  geom_ribbon(alpha = 0.25) +
  facet_grid(
    rows = vars(country),
    cols = vars(measure),
    scales = "free"
  ) +
  prettyplot() +
  scale_colour_manual(values = feed_pal) +
  scale_fill_manual(values = feed_pal) +
  scale_y_continuous(
    name = expression("Loss (kg g"^-1*")"),
    breaks = seq(0, 1, 0.2)
  )
```

```{r}
#| label: uneat-excr-plot-perc-diff

tmp <- ins_tot %>% 
  mutate(t = t-365) %>% 
  merge(farm_geometry, by.x = "farm_ID", by.y = "farm_id") %>% 
  dplyr::select(-c(mean, sd_mean, sd, biom_mean, biom_sd, biom_sd_mean, sd_perbiom)) %>% 
  group_by(country, t, measure) %>% 
  pivot_wider(
    names_from = feed, 
    values_from = mean_perbiom
  ) %>% 
  mutate(
    diff = plant_dominant - marine_dominant,
    perc_diff = diff/plant_dominant
  ) %>%
  group_by(country, t, measure) %>% 
  reframe(
    mean_diff = mean(diff),
    mean_perc_diff = mean(perc_diff),
    sd_diff = sd(diff),
    sd_perc_diff = sd(perc_diff)
  )

tmp <- tmp %>% 
  group_by(measure, country) %>% 
  reframe(
    mean_t_perc_diff = mean(mean_perc_diff),
    sd_t_perc_diff = sd(mean_perc_diff)
    )
```

While the actual difference in excreted and uneaten feed (total loss) varied between countries and through time (@fig-uneat-excr-plot-ts), relative changes between the feeds remained consistent. 
In both the US and Australia (all done so far), total excreted faeces was 
`r round(100*tmp$mean_t_perc_diff[tmp$country == "Australia" & tmp$measure == "total_excr_stat"], 1)`% ($\pm$ `r round(100*tmp$sd_t_perc_diff[tmp$country == "Australia" & tmp$measure == "total_excr_stat"], 1)`%) higher in the plant-dominant feed. 
Differences in total uneaten feed were much smaller at 
`r round(100*-tmp$mean_t_perc_diff[tmp$country == "Australia" & tmp$measure == "total_uneat_stat"], 1)`% ($\pm$ `r round(100*tmp$sd_t_perc_diff[tmp$country == "Australia" & tmp$measure == "total_uneat_stat"], 1)`%) lower in the plant-dominant feed.

### At harvest

```{r}
#| label: uneat-excr-plot-end
#| fig-cap: Caption

ins_tot %>% 
  group_by(farm_ID) %>%
  arrange(farm_ID, t) %>%
  mutate(
    cumsum_mean = cumsum(mean_perbiom) %>% 
      set_units("g g_fish-1") %>% 
      set_units("kg t_fish-1"),
    end_t = max(t)
    ) %>% 
  ungroup() %>% 
  filter(t == end_t) %>% 
  merge(farm_geometry, by.x = "farm_ID", by.y = "farm_id") %>% 
  ggplot(aes(x = country, y = cumsum_mean, fill = feed)) +
  geom_boxplot() +
  facet_grid(cols = vars(measure)) +
  prettyplot() +
  scale_fill_manual(values = feed_pal)
```

## N inputs

```{r}
#| label: N-loss-plot-total
#| fig-cap: Caption

ins_P %>% 
  group_by(farm_ID) %>%
  arrange(farm_ID, t) %>%
  mutate(
    cumsum_mean = cumsum(mean_perbiom)*6.25 %>% 
      set_units("g g_fish-1") %>% 
      set_units("kg t_fish-1"),
    end_t = max(t)
    ) %>% 
  ungroup() %>% 
  filter(t == end_t) %>% 
  merge(farm_geometry, by.x = "farm_ID", by.y = "farm_id") %>% 
  ggplot(aes(x = country, y = cumsum_mean, fill = feed)) +
  geom_boxplot() +
  facet_grid(cols = vars(measure)) +
  prettyplot() +
  scale_fill_manual(values = feed_pal)
```

>>>>

library(magrittr)
library(units)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(ggh4x)
library(here)
library(ggpubr)
library(cowplot)
library(patchwork)
library(qs)
library(arrow)
library(targets)
library(sf)
library(terra)
library(rnaturalearth)
library(rnaturalearthdata)
library(rnaturalearthhires)
library(dtplyr)
library(furrr)
library(purrr)
library(future)
library(readxl)
library(conflicted)
library(lubridate)
library(RColorBrewer)
# library(lme4)
library(car)
library(emmeans)

conflicts_prefer(dplyr::select(), dplyr::filter(), dplyr::intersect())
# This markdown uses TinyTex - install with tinytex::install_tinytex()

@@

```{r}
#| label: global-variables
#| include: false
#| cache: false

@@

long_feeds <- c("marine_dominant", "plant_dominant", "novel_inclusive")
short_feeds <- c("MD", "PD", "NI")

feed_pal <- c(
  "past" = "#E41A1C", 
  "reference" = "#377EB8", 
  "future" = "#4DAF4A",
  "plant_dominant" = "#4DAF4A",
  "marine_dominant" = "#377EB8",
  "novel_inclusive" = "#E41A1C",
  "PD" = "#4DAF4A",
  "MD" = "#377EB8",
  "NI" = "#E41A1C"
)
cohort_pal <- c("1" = "#E41A1C", "2" = "#377EB8", "3" = "#4DAF4A", "all" = "black")
macro_pal <- c(
  "protein" = "darkred", 
  "P" = "darkred", 
  "carbohydrates" = "steelblue", 
  "C" = "steelblue", 
  "lipids" = "darkgoldenrod1", 
  "L" = "darkgoldenrod1"
)

@@

```{r}
#| label: load-all-data-analysis

# Biomass produced
bpr1 <- find_read(output_model_farm_path, "biomass_produced") %>% 
  mutate(feed = factor(feed, levels = long_feeds, labels = short_feeds)) %>% 
  group_by(feed) %>% 
  reframe(mean = mean(mean) %>% set_units("g") %>% set_units("t") %>% drop_units() %>% round(1)) %>% 
  pivot_wider(names_from = feed, values_from = mean)

bpr2 <- find_read(comparisons_path, "biomass_produced") %>% 
  group_by(feed) %>% 
  reframe(diff = (100*mean(mean)) %>% round(1)) %>% 
  pivot_wider(names_from = feed, values_from = diff)

# Feed provided
fpr1 <- find_read(data_analysis_path, "food_prov_farm_summed") %>% 
  mutate(feed = factor(feed, levels = long_feeds, labels = short_feeds)) %>% 
  group_by(feed) %>% 
  reframe(total = mean(total) %>% set_units("g") %>% set_units("t") %>% drop_units() %>% round(1)) %>% 
  pivot_wider(names_from = feed, values_from = total)

fpr2 <- find_read(comparisons_path, "food_prov_farm_summed") %>% 
  group_by(feed) %>% 
  reframe(diff = (100*mean(total)) %>% round(1)) %>% 
  pivot_wider(names_from = feed, values_from = diff)

# Feed provided per biomass
fpr_pb1 <- find_read(data_analysis_path, "food_prov_farm_per_biom_summed") %>% 
  mutate(feed = factor(feed, levels = long_feeds, labels = short_feeds)) %>% 
  group_by(feed) %>% 
  reframe(mean_biom = mean(mean_biom) %>% set_units("g g_fish-1") %>% set_units("kg kg_fish-1") %>% drop_units() %>% round(2)) %>% 
  pivot_wider(names_from = feed, values_from = mean_biom)

fpr_pb2 <- find_read(comparisons_path, "food_prov_farm_per_biom_summed") %>% 
  group_by(feed) %>% 
  reframe(diff = (100*mean(mean_biom)) %>% round(1)) %>% 
  pivot_wider(names_from = feed, values_from = diff)

# Uneaten feed
tuf1 <- find_read(data_analysis_path, "total_uneat_farm_summed") %>% 
  mutate(feed = factor(feed, levels = long_feeds, labels = short_feeds)) %>% 
  group_by(feed) %>% 
  reframe(total = mean(total) %>% set_units("g") %>% set_units("t") %>% drop_units() %>% round(1)) %>% 
  pivot_wider(names_from = feed, values_from = total)

tuf2 <- find_read(comparisons_path, "total_uneat_farm_summed") %>% 
  group_by(feed) %>% 
  reframe(diff = (100*mean(total)) %>% round(1)) %>% 
  pivot_wider(names_from = feed, values_from = diff)

# Excreted waste
tew1 <- find_read(data_analysis_path, "total_excr_farm_summed") %>% 
  mutate(feed = factor(feed, levels = long_feeds, labels = short_feeds)) %>% 
  group_by(feed) %>% 
  reframe(total = mean(total) %>% set_units("g") %>% set_units("t") %>% drop_units() %>% round(1)) %>% 
  pivot_wider(names_from = feed, values_from = total)

tew2 <- find_read(comparisons_path, "total_excr_farm_summed") %>% 
  group_by(feed) %>% 
  reframe(diff = (100*mean(total)) %>% round(1)) %>% 
  pivot_wider(names_from = feed, values_from = diff)

# Total waste
tow1 <- find_read(data_analysis_path, "total_mass_inputs_farm_summed") %>% 
  # mutate(feed = factor(feed, levels = long_feeds, labels = short_feeds)) %>% 
  group_by(feed) %>% 
  reframe(total = mean(total) %>% set_units("g") %>% set_units("t") %>% drop_units() %>% round(1)) %>% 
  pivot_wider(names_from = feed, values_from = total)

tow2 <- find_read(comparisons_path, "total_mass_inputs_farm_summed") %>% 
  group_by(feed) %>% 
  reframe(diff = (100*mean(total)) %>% round(1)) %>% 
  pivot_wider(names_from = feed, values_from = diff)

# Excretion proportion of waste
epw <- find_read(comparisons_path, "excr_proportion_of_waste") %>% 
  group_by(feed) %>% 
  reframe(diff = (100*mean(total)) %>% round(1)) %>% 
  pivot_wider(names_from = feed, values_from = diff)

# Protein, lipid, carbs
plc1 <- find_read(data_analysis_path, "PLC_uneat_excr_farm_summed") %>% 
  # mutate(feed = factor(feed, levels = long_feeds, labels = short_feeds)) %>% 
  group_by(feed, measure, macro) %>% 
  reframe(total = mean(total) %>% set_units("g") %>% set_units("t") %>% drop_units() %>% round(1)) %>% 
  pivot_wider(names_from = c(feed, macro), values_from = total)

# Proportion of PLC waste from excretion
plc2 <- find_read(data_analysis_path, "PLC_uneat_excr_farm_summed") %>% 
  # mutate(feed = factor(feed, levels = long_feeds, labels = short_feeds)) %>% 
  group_by(feed, measure, macro) %>% 
  reframe(total = mean(total) %>% set_units("g") %>% set_units("t") %>% drop_units() %>% round(1)) %>% 
  pivot_wider(names_from = c(feed, macro, measure), values_from = total) %>% 
  mutate(
    MD_C = round(100*MD_C_excr/(MD_C_excr+MD_C_uneat),1),
    MD_L = round(100*MD_L_excr/(MD_L_excr+MD_L_uneat),1),
    MD_P = round(100*MD_P_excr/(MD_P_excr+MD_P_uneat),1),
    NI_C = round(100*NI_C_excr/(NI_C_excr+NI_C_uneat),1),
    NI_L = round(100*NI_L_excr/(NI_L_excr+NI_L_uneat),1),
    NI_P = round(100*NI_P_excr/(NI_P_excr+NI_P_uneat),1),
    PD_C = round(100*PD_C_excr/(PD_C_excr+PD_C_uneat),1),
    PD_L = round(100*PD_L_excr/(PD_L_excr+PD_L_uneat),1),
    PD_P = round(100*PD_P_excr/(PD_P_excr+PD_P_uneat),1)
  ) %>% 
  select(-contains(c("excr", "uneat")))

# % change in PLC waste
plc3 <- find_read(comparisons_path, "PLC_uneat_excr_farm_summed") %>% 
  group_by(feed, macro) %>% 
  reframe(diff = (100*mean(total)) %>% round(1)) %>% 
  pivot_wider(names_from = c(feed, macro), values_from = diff)

# N inputs, uneaten
niu1 <- find_read(data_analysis_path, "P_uneat_farm_summed") %>% 
  mutate(feed = factor(feed, levels = long_feeds, labels = short_feeds),
         total = total * 6.25,
         sd = sd * 6.25) %>% 
  group_by(feed) %>% 
  reframe(total = mean(total) %>% set_units("g") %>% set_units("t") %>% drop_units() %>% round(1)) %>% 
  pivot_wider(names_from = feed, values_from = total)

niu2 <- find_read(comparisons_path, "N_uneat_farm_summed") %>% 
  group_by(feed) %>% 
  reframe(diff = (100*mean(total)) %>% round(1)) %>% 
  pivot_wider(names_from = feed, values_from = diff)

# N inputs, excreted
nie1 <- find_read(data_analysis_path, "P_excr_farm_summed") %>% 
  mutate(feed = factor(feed, levels = long_feeds, labels = short_feeds),
         total = total * 6.25,
         sd = sd * 6.25) %>% 
  group_by(feed) %>% 
  reframe(total = mean(total) %>% set_units("g") %>% set_units("t") %>% drop_units() %>% round(1)) %>% 
  pivot_wider(names_from = feed, values_from = total)

nie2 <- find_read(comparisons_path, "N_excr_farm_summed") %>% 
  group_by(feed) %>% 
  reframe(diff = (100*mean(total)) %>% round(1)) %>% 
  pivot_wider(names_from = feed, values_from = diff)

# N inputs, total
nit1 <- find_read(data_analysis_path, "N_total_farm_summed.qs") %>% 
  # mutate(feed = factor(feed, levels = long_feeds, labels = short_feeds)) %>% 
  group_by(feed) %>% 
  reframe(total = mean(total) %>% set_units("g") %>% set_units("t") %>% drop_units() %>% round(1)) %>% 
  pivot_wider(names_from = feed, values_from = total)

nit2 <- find_read(comparisons_path, "N_total_farm_summed.qs") %>% 
  group_by(feed) %>% 
  reframe(diff = (100*mean(total)) %>% round(1)) %>% 
  pivot_wider(names_from = feed, values_from = diff)
```

@tbl-results-summary is a summary of all the results I've processed so far, basically trying to acertain all the major differences in inputs between the feeds.

| Description | Plant-dominant | Marine-dominant | Novel-inclusive | Change from PD to MD (%) | Change from PD to NI (%) |
|:--------------------------|:----------:|:----------:|:----------:|:----------:|:----------:|
| Salmon biomass produced (t) | `r bpr1$PD` | `r bpr1$MD` | `r bpr1$NI` | `r bpr2$MD` | `r bpr2$NI` |
| Feed provided (t) | `r fpr1$PD` | `r fpr1$MD` | `r fpr1$NI` | `r fpr2$MD` | `r fpr2$NI` |
| Feed provided (kg/kg salmon) | `r fpr_pb1$PD` | `r fpr_pb1$MD` | `r fpr_pb1$NI` | `r fpr_pb2$MD` | `r fpr_pb2$NI` |
| Uneaten feed (t) | `r tuf1$PD` | `r tuf1$MD` | `r tuf1$NI` | `r tuf2$MD` | `r tuf2$NI` |
| Excreted waste (t) | `r tew1$PD` | `r tew1$MD` | `r tew1$NI` | `r tew2$MD` | `r tew2$NI` |
| Total waste (E+U, t) | `r tow1$PD` | `r tow1$MD` | `r tow1$NI` | `r tow2$MD` | `r tow2$NI` |
| Proportion of total waste composed of excretion (%) | `r epw$PD` | `r epw$MD` | `r epw$NI` |  |  |
| Total protein waste (t) | `r sum(plc1$PD_P)` | `r sum(plc1$MD_P)` | `r sum(plc1$NI_P)` | `r plc3$MD_P` | `r plc3$NI_P` |
| Total carbohydrate waste (t) | `r sum(plc1$PD_C)` | `r sum(plc1$MD_C)` | `r sum(plc1$NI_C)` | `r plc3$MD_C` | `r plc3$NI_C` |
| Total lipid waste (t) | `r sum(plc1$PD_L)` | `r sum(plc1$MD_L)` | `r sum(plc1$NI_L)` | `r plc3$MD_L` | `r plc3$NI_L` |
| Proportion of protein waste from excretion (%) | `r plc2$PD_P` | `r plc2$MD_P` | `r plc2$NI_P` |  |  |
| Proportion of carbohydrate waste from excretion (%) | `r plc2$PD_C` | `r plc2$MD_C` | `r plc2$NI_C` |  |  |
| Proportion of lipid waste from excretion (%) | `r plc2$PD_L` | `r plc2$MD_L` | `r plc2$NI_L` |  |  |
| Total N from uneaten feed (t) | `r niu1$PD` | `r niu1$MD` | `r niu1$NI` | `r niu2$MD` | `r niu2$NI` |
| Total N from excreted waste (t) | `r nie1$PD` | `r nie1$MD` | `r nie1$NI` | `r nie2$MD` | `r nie2$NI` |
| Total N inputs (E+U, t) | `r nit1$PD` | `r nit1$MD` | `r nit1$NI` | `r nit2$MD` | `r nit2$NI` |
: Summary of all results. Unless otherwise specified, values presented are means across all farms, summed across a single production period. Some cells of this table are blank - sometimes that means it doesn't make sense to fill that cell, but sometimes it means I haven't got to it yet. {#tbl-results-summary}

So here are the major themes I'm getting from @tbl-results-summary:

::: {.aside}
*Note that when I refer to "FCE" here I'm talking about the PLC weight (protein + lipid + carbohydrate) weight of feed, which may differ from its actual weight because of the inclusion of minerals and non-digestible material.
:::

1. The NI diet was more efficient than the PD diet. When farms were fed the NI diet they had an average FCE* of `r fpr_pb1$NI`, compared to the average FCE of `r fpr_pb1$PD` when farms were fed the PD diet, and feeding the NI diet resulted in `r bpr2$NI`% more biomass produced with the same population compared to the PD diet.
2. Despite this, nutrients lost to the environment were generally highest in the NI diet and lowest in the MD diet. 
  * In terms of total waste inputs (bulk mass), the NI and PD diets were very similar (probably due to their very similar ingredient compositions). The MD diet had markedly lower total waste inputs than either the PD or NI diets.
3. However, the PLC composition of nutrients was very different between the diets (@fig-PLC-waste-comparison). The PD diet had the lowest protein waste output and the NI diet had the highest, while the MD diet had the lowest carbohydrate and lipid waste outputs and the PD diet the highest. Overall, changing from the PD diet to the NI diet would result in a `r abs(plc3$NI_P)`% increase in protein waste but a `r abs(plc3$NI_C)`% and `r abs(plc3$NI_L)`% reduction in carbohydrates and lipids respectively, while changing to the MD diet would result in a `r abs(plc3$MD_P)`% increase in protein waste but a `r abs(plc3$NI_C)`% and `r abs(plc3$NI_L)`% reduction in carbohydrates and lipids respectively.
4. Overall, nitrogen inputs were `r nit2$NI`% higher in the NI diet and `r nit2$MD`% higher in the MD diet.

```{r}
#| label: PLC-waste-comparison

plc1 <- find_read(data_analysis_path, "PLC_uneat_excr_farm_summed")

lm_P <- lm(drop_units(total) ~ feed * measure, data = filter(plc1, macro == "P"))
aov_P <- aov(lm_P)
# summary(aov_P)

emm <- emmeans(lm_P, "feed", "measure")
tukey_results <- pairs(emm, adjust = "tukey")
# print(tukey_results)

lm_C <- lm(drop_units(total) ~ feed * measure, data = filter(plc1, macro == "C"))
aov_C <- aov(lm_C)
# summary(aov_C)

emm <- emmeans(lm_C, "feed", "measure")
tukey_results <- pairs(emm, adjust = "tukey")
# print(tukey_results)

lm_L <- lm(drop_units(total) ~ feed * measure, data = filter(plc1, macro == "L"))
aov_L <- aov(lm_L)
# summary(aov_L)

emm <- emmeans(lm_L, "feed", "measure")
tukey_results <- pairs(emm, adjust = "tukey")
# print(tukey_results)
```

```{r}
#| label: fig-PLC-waste-comparison
#| fig-cap: Mean waste lost to the environment in a complete production cycle when farms are fed the MD (blue), PD (green) or NI (red) diet. Errorbars show SD across all farms.

plc1 %>%
  group_by(measure, macro, feed) %>%
  reframe(
    sd = sd(total) %>% set_units("g") %>% set_units("t") %>% drop_units(),
    total = mean(total) %>% set_units("t") %>% drop_units(), 
  ) %>% 
  mutate(
    macro = factor(
      macro, 
      levels = c("P", "C", "L"),
      labels = c("Protein", "Carbohydrate", "Lipid")
    ),
    measure = factor(
      measure,
      levels = c("excr", "uneat"),
      labels = c("Excreted", "Uneaten")
    )
  ) %>% 
  ggplot(aes(
    x = measure, 
    y = total, 
    ymin = total-sd, ymax = total+sd,
    fill = feed
  )) +
  geom_col(position = position_dodge(), width = 0.95, colour = "black") +
  geom_errorbar(position = position_dodge(width = 0.95), width = 0.5) +
  facet_grid(cols = vars(macro)) +
  prettyplot() +
  scale_fill_manual(values = feed_pal) +
  labs(y = "Mean total waste (t)", x = "Source")
```

# Spatially

```{r}
#| label: fig-spatial-PLC
#| fig-height: 12
#| fig-cap: Total N inputs per unit biomass of salmon produced when farms are fed the MD feed (top), the PD feed (middle) or the NI feed (bottom).

plc1 <- find_read(comparisons_path, "PLC_uneat_excr_farm_summed")

N_ins <- rbind(
  find_read(data_analysis_path, "P_excr_farm_per_biom_summed"),
  find_read(data_analysis_path, "P_uneat_farm_per_biom_summed")
) %>% 
  st_drop_geometry() %>% 
  mutate(feed = factor(feed, levels = long_feeds, labels = short_feeds)) %>% 
  group_by(country, farm_ID, feed) %>% 
  reframe(
    mean_biom = sum(mean_biom) %>% set_units("kg t_fish-1") %>% drop_units(), 
    sd_biom = sqrt(sum(sd_biom^2)) %>% set_units("g g_fish-1") %>% set_units("kg t_fish-1") %>% drop_units()
  ) %>% 
  merge(farm_locs, by = c("country", "farm_ID")) %>% 
  st_as_sf()

p_bigmap_robinson +
  geom_sf(
    data = N_ins, 
    aes(colour = mean_biom, geometry = geometry), 
    size = 2
  ) +
  coord_sf() +
  scale_color_viridis_c(option = "turbo", breaks = seq(0, 120, 10)) + 
  guides(col = guide_colourbar(
    title = expression("Total N inputs (kg/t salmon)"),
    direction = "horizontal", position = "bottom",
    label.position = "bottom", title.position = "top",
    title.vjust = 1, title.hjust = 0.5,
    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 1.5,
    barheight = 1.5, barwidth = 20,
  )) +
  facet_grid(rows = vars(feed)) +
  prettyplot() +
  theme(strip.background = element_blank(), strip.text = element_blank(),
        axis.title = element_blank(),
        legend.position = "bottom")
```

```{r}
#| label: protein-inputs-patchwork-map

p_mercator <- p_bigmap_mercator +
  geom_sf(
    data = N_ins,
    aes(colour = mean_biom, geometry = geometry), 
    size = 2.5
  ) +
  coord_sf() +
  scale_color_viridis_c(option = "turbo", breaks = seq(0, 120, 10)) + #, limits = c(-30, 10)
  guides(col = guide_colourbar(
    title = expression("Total N inputs (kg/t salmon)"),
    direction = "horizontal", position = "bottom",
    label.position = "bottom", title.position = "top",
    title.vjust = 1, title.hjust = 0.5,
    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 1.5,
    barheight = 1.5, barwidth = 20,
  )) +
  # facet_wrap(facets = vars(feed), nrow = 2, ncol = 2) +
  prettyplot() +
  theme(
    # strip.background = element_blank(), strip.text = element_blank(),
    legend.position = "bottom"
  ) +
  labs(y = "Latitude", x = "Longitude")

ins <- get_insets_mercator(p_mercator)

ins[[1]] + facet_grid(cols = vars(feed))
ins[[2]] + facet_grid(rows = vars(feed))
ins[[3]] + facet_grid(cols = vars(feed))
ins[[4]] + facet_grid(cols = vars(feed))
ins[[5]] + facet_grid(cols = vars(feed))
```

@@

```{r}
#| label: fig-sensitivity-results
#| fig-cap: Sensitivity of modelled individual fish weight (blue) and total farm excretion across a full production period (red) to a 10% increase in each model parameter. Bars show mean values, error bars show standard deviation between farms. 
#| fig-width: 8

sens_results <- find_read(output_sens_data_path, "sens_results") %>% 
  filter(measure %in% c("total_excr", "weight") & adj_param != "nruns") %>% 
  mutate(measure = droplevels(measure))

sens_results %>% 
  ggplot(aes(x = adj_param, y = mean_sens, ymin = mean_sens-sd_sens, ymax = mean_sens+sd_sens, fill = measure)) +
  geom_col(position = position_dodge(), width = 0.95, alpha = 0.65, colour = "black") +
  geom_errorbar(position = position_dodge(width = 0.95), width = 0.5) +
  coord_flip() +
  prettyplot() +
  scale_x_discrete(breaks = param_names$name, labels = param_names$lab) +
  scale_y_continuous(breaks = seq(-10, 30, 5)) +
  scale_fill_brewer(palette = "Set1") +
  labs(y = "Sensitivity", x = "Adjusted parameter")
```
